\documentstyle[11pt]{article}
\pagestyle{empty} \setlength{\topmargin}{-.5in}
\addtolength{\textheight}{2in} \addtolength{\oddsidemargin}{-1in}
\addtolength{\textwidth}{2in} \setlength{\parindent}{0pt}
\begin{document}
* \vfill
\Large{
\begin{center}Math 307\\
Discrete Mathematics\\
Exam I\\
29 September 2003\\
\vspace{1in} Name:{\underline{\hspace{2in}}}\\\end{center}

\vspace{1in} There are nine questions worth a total of 100 points.
Use standard notation (like what is used in class and in the text).
This exam is closed note and closed book. No calculators are
allowed.

\vfill *

\newpage
\begin{enumerate}
\item (10 points) Evaluate $P(10,2) \cdot C(9,7).$
\vspace{1in}

\item (10 points) Construct the truth table for the compound proposition
$$( p \vee q) \rightarrow ( \neg r \underline{\vee} p)$$
\vfill




\item (10 points) Rewrite each of the following statements as an implication
in the {\bf if-then} form. \begin{enumerate} \item Today is Tuesday
only if it is snowing. \vspace{1in} \item Sunshine is a necessary
condition for the chair to be blue. \vspace{1in}
\end{enumerate}

\newpage
\item (10 points) \begin{enumerate} \item How many different ways are there
 to arrange the letters in the word: MISSISSIPPI ? \vspace{1in}
\item How many different ways are there to arrange the letters in the
word MISSISSIPPI so that no I is adjacent to another I? \vspace{2in}
\end{enumerate}


\item (10 points) Evaluate the sum:
$$2^n -2^{n-1}{n \choose 1}+2^{n-2}{n \choose 2}- \cdots +(-1)^{n-1}2{n \choose n-1}+(-1)^n$$
\vfill
\newpage

\item (10 points) Consider all strings of length seven made up from the
alphabet: 0,1, and 2. \begin{enumerate} \item How many distinct strings are possible?
\vfill \item How many different strings have a weight of four? \vfill\end{enumerate}


\item (15 points) Problems (a), (b), and (c) below refer to a barrel
of red, blue, yellow, and green marbles where there are exactly 20
marbles of each color. (So, 80 marbles total.) \begin{enumerate}
\item In how many ways can 10 marbles be permuted (that is, arranged in a line)
 if all 80 marbles
are considered distinct?\vfill
\item In how many ways can 10 marbles be selected (without order) if
the marbles of the same color are considered identical? \vfill
\item Repeat part (b) assuming you want at least one marble of each of the four colors.
\vfill\end{enumerate}
\newpage

\item (15 points) A department has 10 math faculty, 15 computer science faculty,
and 5 statistics faculty. How many different 4-person committees are possible if:
\begin{enumerate} \item there are no restrictions? \vfill
\item the committee must contain at least one computer science faculty? \vfill
\item the committee must contain at least one member from each area? \vfill \end{enumerate}

\item (10 points) Four children ($C_1,C_2,C_3,C_4$) each bring one of their
parents\\
\noindent ($P_1,P_2,P_3,P_4$) to a luncheon. All eight people sit
around a single round table. Assume that rotations of the table give
the same seating arrangement. How many different ways can they sit
at the table if:\begin{enumerate}
\item there are no restrictions? \vfill
\item Child One ($C_1$) refuses to sit next to her parent, ($P_1$)?\vfill
\item every parent must sit next to his/her child? (That is,
$P_i$ must sit next to $C_i$ for all $1 \leq i \leq 4.$)\vfill\end{enumerate}

\end{enumerate}
}\end{document}
