%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% This top part of the document is called the 'preamble'.  Modify it with caution!
%
% The real document starts below where it says 'The main document starts here'.

\documentclass[12pt]{article}

\usepackage{amssymb,amsmath,amsthm}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumerate}
%for the picture. 
\usepackage{tikz, calc}
%% The next line says how the "vertex" style of nodes should look: drawn as small circles.
\tikzstyle{vertex}=[circle, draw, inner sep=3pt, minimum size=6pt]
%%
%% Next, we make a \vertex command as a shorthand in place of \node[vertex} to get that style.
\newcommand{\vertex}{\node[vertex]}
% Comment the following line to use TeX's default font of Computer Modern.
\usepackage{times,txfonts}

\newtheoremstyle{homework}% name of the style to be used
  {18pt}% measure of space to leave above the theorem. E.g.: 3pt
  {12pt}% measure of space to leave below the theorem. E.g.: 3pt
  {}% name of font to use in the body of the theorem
  {}% measure of space to indent
  {\bfseries}% name of head font
  {:}% punctuation between head and body
  {2ex}% space after theorem head; " " = normal interword space
  {}% Manually specify head
\theoremstyle{homework} 

% Set up an Exercise environment and a Solution label.
\newtheorem*{exercisecore}{Exercise \@currentlabel}
\newenvironment{exercise}[1]
{\def\@currentlabel{#1}\exercisecore}
{\endexercisecore}

\newcommand{\localhead}[1]{\par\smallskip\noindent\textbf{#1}\nobreak\\}%
\newcommand\solution{\localhead{Solution:}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Stuff for getting the name/document date/title across the header
\makeatletter
\RequirePackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\ifnum \value{page} > 1\relax\thepage\fi}
\fancyhead[L]{\ifx\@doclabel\@empty\else\@doclabel\fi}
\fancyhead[C]{\ifx\@docdate\@empty\else\@docdate\fi}
\fancyhead[R]{\ifx\@docauthor\@empty\else\@docauthor\fi}
\headheight 15pt

\def\doclabel#1{\gdef\@doclabel{#1}}
\doclabel{Use {\tt\textbackslash doclabel\{MY LABEL\}}.}
\def\docdate#1{\gdef\@docdate{#1}}
\docdate{Use {\tt\textbackslash docdate\{MY DATE\}}.}
\def\docauthor#1{\gdef\@docauthor{#1}}
\docauthor{Use {\tt\textbackslash docauthor\{MY NAME\}}.}
\makeatother

% Shortcuts for blackboard bold number sets (reals, integers, etc.)
\newcommand{\Reals}{\ensuremath{\mathbb R}}
\newcommand{\Nats}{\ensuremath{\mathbb N}}
\newcommand{\Ints}{\ensuremath{\mathbb Z}}
\newcommand{\Rats}{\ensuremath{\mathbb Q}}
\newcommand{\Cplx}{\ensuremath{\mathbb C}}
%% Some equivalents that some people may prefer.
\let\RR\Reals
\let\NN\Nats
\let\II\Ints
\let\CC\Cplx

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% The main document start here.

% The following commands set up the material that appears in the header.
\doclabel{Graph Theory: Review for Midterm I}
\docauthor{}
\docdate{\date}

\begin{document}
\noindent \textbf{terminology and notation}\\

\fbox{1.1}  graph, vertex set, edge set, endpoints, loop, multiple edges, adjacent, neighbors, complement, clique, independent set, stable set, bipartite graph, subgraph, connected, disconnected, isomorphism, isomorphism class


\fbox{1.2}  walk, trail, path, internal vertices of a walk/trail/path, endpoints of a walk/trail/path, length, closed, components, isolated vertex, cut-edge, cut-vertex, induced subgraph, bipartition, $X,Y$-bigraph, Eulerian circuit, Eulerian graph, even graph, maximal path, maximum path, $C_k$, $P_k$, $K_n$, $K_{n,m}$, biclique, Petersen graph

\fbox{1.3} degree of a vertex, $d_G(v)$, $\Delta(G)$, $\delta(G)$, maximum degree, minimum degree, $k$-regular graph, $N_G(v)$, order, size, $n(G)$, $e(G)$, degree sequence, graphic sequence

\fbox{2.1} acyclic, forest, tree, leaf, pendant vertex, spanning subgraph, spanning tree, star, distance, $d_G(u,v)$, diameter, $diam(G)$, eccentricity, $\epsilon(v)$, radius, $rad(G)$, center

\vspace{.3in}

\noindent \textbf{major theorems / useful results}\\

\fbox{1.2}\\
Every $uv$-walk contains a $uv$-path.\\
Every graph with $n$ vertices and $k$ edges contains at least $n-k$ components.\\
An edge is a cut-edge iff it lies on a cycle.\\
A graph is bipartite iff it has no odd cycle.\\
A graph is Eulerian iff it has at most one nontrivial component and all vertices have even degree.\\
Even graphs decompose into cycles.\\
Every graph with a nonloop edge has at least two vertices that are not cut-vertices.\\

\fbox{1.3}\\
The Degree-Sum Formula\\
A $k$-regular bipartite graph has the same number of vertices in each partite set.\\
If the $n$-vertex graph $G$ has $\delta(G) \geq (n-1)/2,$ then $G$ must be connected.\\
The minimum number of edges in an $n$-vertex graph is $\lfloor n^2/4 \rfloor.$\\
For every degree sequence with an even sum, there is a (multi)graph that realizes that sequence.\\
Havel-Hakimi Theorem and implied algorithm\\

\fbox{2.1}\\
Every tree with at least two vertices has at least two leaves.\\
Deleting a leaf from a tree on at least two vertices gives a tree on $n-1$ vertices.\\
A list of equivalent definitions of a tree.\\
Adding a single edge to a tree produces a unique cycle.\\
Every connected graph contains a spanning tree.\\
If $G$ is a simple graph with $diam(G) \geq 3$, then $diam(\overline{G}) \leq 3$\\
The center of a tree is $K_1$ or $K_2.$\\
If $H \subseteq G$, then for every $u,v \in V(H)$ $d_H(u,v) \geq d_G(u,v).$

\newpage

Taking a test in a proof-centric course

\begin{itemize}
\item \textbf{Know the formal definitions.} You will need these to start any proof. Example: Show that if the graph $G$ is connected, then ...
\item \textbf{Know the major results and homework problems.} You are allowed to use these \textit{unless explicitly directed not to}. Example: Show the graph $G$ is bipartite. OR Use the definition of bipartite to show the graph $G$ is bipartite. 
\item It is better to not complete a proof/question than to draw what is obviously an incorrect conclusion. Example: Show $G$ is connected. Answer: Here is a path from the vertex $u$ to the vertex $v$, so $G$ is connected.
\item When in doubt, work the ends against the middle. Example: If $X$, then $Y$.
\item \textbf{Know major proof techniques.}
\end{itemize}
\end{document}


