\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}


% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
\usepackage{soul}

\newcommand{\blankbox}[2]{\fbox{\rule{#1}{0in}\rule{0in}{#2}}}
%special commands for number sets
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
%special commands for formatting: center, enumerate, pmatrix, vector span
\def\bc{\begin{center}}
\def\ec{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\spn}[1]{\text{Span}\left\{#1\right\}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\llra}{\longleftrightarrow}

\setlength{\headheight}{30pt}
\setlength{\headsep}{20pt}
\setlength{\fboxsep}{8pt}
\setlength{\fboxrule}{1pt}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

%header
\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 265: Exam 1 Review}}
\rhead{\large\sf\textbf{Spring 2026}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}
\begin{document}
\thispagestyle{fancy}

Exam 1 will be on Friday 6 February during our regular class time. So you will have one hour to complete the exam. Notes, books and other aids are not allowed.\\

\begin{center} Chapter 1: Sets\end{center}
Section 1
\begin{itemize}
\item Terms to know: element of a set, cardinality of a set, set builder notation, natural numbers, integers, rational numbers, real numbers, interval notation
\item Symbols to know $\NN,\: \ZZ,\: \QQ, \RR, \in$ and basic set notation
\item You should know how to go back and forth between different kinds of set notation.
\end{itemize}
Section 2
\begin{itemize}
\item terms to know: ordered pair, Cartesian product, ordered $n$-tuple
\item symbols to know: $A \times B$
\item You should know how to count the number of elements in $A \times B$ provided $A$ and $B$ are finite.
\item Know how to sketch $A \times B \subseteq \RR \times \RR$
\end{itemize}
Sections 3 and 4
\begin{itemize}
\item terms to know: subset, the power set of a set
\item symbols to know: $\subseteq$, $\mathcal{P}(A)$
\item Know how to distinguish between $A \in B$ or $A \subseteq B.$
\item Know how to determine the cardinality of the power set of a finite set.
\end{itemize}
Sections 5 and 6
\begin{itemize}
\item Know how to find the union, intersection, and difference of two sets.
\item symbols to know: $\cup, \: \cap, \: -$ and $\overline{A}$.
\item Know how to find the complement of a set.
\end{itemize}
Section 7
\begin{itemize}
\item Know now to draw and to read a Venn diagram.
\end{itemize}
Section 8
\begin{itemize}
\item terms to know: indexed sets
\item notation to know: $\displaystyle{\bigcup_{i \in I} A_i}$, $\displaystyle\bigcap_{i \in I} A_i$
\end{itemize}

\begin{center} Chapter 2: Logic \end{center}

\begin{itemize}
\item terms to know: statement, the mathematical meaning of \emph{and, or} and \emph{not}, truth table, conditional statement, biconditional, quantifiers
\item symbols to know: $\vee,\: \wedge,\: \sim,\: \Leftarrow, \: \Leftrightarrow, \: \forall, \: \exists$
\item You need to be familiar with \emph{alternate} formulations of these logical statements in English. (See especially the bottom of page 44.) You should be able to go back and forth between a compound statement in English and one in symbolic logic.
\item Know how to decide if a statement with \emph{and}, \emph{or} or \emph{not} is true or false.
\item Know how to decide if a conditional, biconditional, or quantified statement is true or false.
\item Know how to determine if two statements are logically equivalent or not.
\item Know DeMorgan's Laws (page 51).
\item Know how to determine if an argument is or is not valid.
\end{itemize}
\end{document}

\begin{center} Definitions \end{center}

For all of the terms below, you must be able to formally state the definition from your textbook. 
\be
\item odd, even, same parity, opposite parity
\item divides, multiple, divisor
\item prime
\item greatest common divisor, least common multiple
\item congruent modulo $n$
\item rational number, irrational number
\ee

\begin{center} Proof Techniques \end{center}
\be
\item direct proof
\item using cases
\item by contrapositive
\item by contradiction
\ee

\begin{center} Things to Keep in Mind \end{center}
\be
\item If a proof technique is not prescribed, you MUST state the method you are using.
\item You should put in the ``boiler-plate'' language even if you cannot figure out the whole proof.
\item You should expect to \emph{use} all of the hypotheses.
\item I will \emph{not} ask you to prove something that is false.
\ee
\end{document}