\documentclass[11pt]{article}
\setlength{\topmargin}{-0.8in} % usually -0.25in
\addtolength{\textheight}{1.4in} % usually 1.25in
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.8in}
\addtolength{\textwidth}{1.6in} %\setlength{\parindent}{0pt}

\usepackage[T1]{fontenc} % Recommended for better encoding
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}

% macros
\usepackage{amsmath,
amssymb,
mathrsfs,
amsthm,
fancyhdr,
tikz,
multicol,
enumitem
}

\newcommand{\be}{\begin{enumerate}}
 \newcommand{\ee}{\end{enumerate}}


\newcommand{\C}{{\mathbb{C}}}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\eps}{\epsilon}
\newcommand{\Z}{{\mathbb{Z}}}
\newcommand{\Q}{{\mathbb{Q}}}
\newcommand{\N}{{\mathbb{N}}}



\lhead{{Math 265 Proofs}}
\chead{\large \ Midterm II} 
\rhead{Spring 2026}
\cfoot{}
\pagestyle{fancy}
\begin{document}
\thispagestyle{fancy}


\medskip
\large
\vspace{.1in}
\begin{tabular}{l@{\hspace{.4in}}l}
Your Name & \\
\framebox(200,30){} &  \\
\end{tabular}

%\bigskip

\vfill
{
\renewcommand{\baselinestretch}{1.8}
\setlength{\tabcolsep}{.2in}
\normalsize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Problem&Total Points&\parbox{.8in}{\hfil Score\hfil}\\
\hline
1&15&\\
\hline
2&15&\\
\hline
3&15&\\
\hline
4&20&\\
\hline
5&15&\\
\hline
6&20&\\
\hline
%\hline
Total&100&\\
\hline

\end{tabular}

\end{center}
}
\vfill
\begin{itemize}
\item 
You have 1 hour.

\item If you have a cell phone with you, it should be turned off and put away. (Not in your pocket)

\item You may not use a calculator, book, notes or aids other than a single 3 by 5 notecard.

\item In order to lower the writing load, you may use the symbols $\in$, $\exists$, and $\forall$ \emph{if} they are used precisely and literally. You will not be graded on aesthetics, so repeated use of "Thus, ..." will not be penalized. 
\item You may \emph{not} use the symbol $\Rightarrow$ except parenthetically to indicate the logical structure of an \emph{if-and-only-if} argument. 
\item You must write in complete sentences with proper punctuation. Every sentence must begin with a capitalized word in English, not a symbol. 
\item If you are going to use a method \emph{other than a direct proof}, you must state this at the beginning of your proof unless the directions require you to use particular approach.
\end{itemize}
\newpage
\begin{enumerate}
%Set builder notation
\item (15 pts) Give a \textbf{direct} proof of the statement below.
\begin{quote} For every real number x, if $x \geq -1,$ then there exists some real number $y$ such that $y^2-1=x.$ \end{quote}

\newpage

\item (15 points) Give a proof by \textbf{contrapositive} of the statement below.

\begin{quote} For every pair of integers $a$ and $b$, if $(a+1)(6a+b)$ is odd, then $a$ is even and $b$ is odd. \end{quote}
\vfill
\newpage
\item (15 points) Give a proof by \textbf{contradiction} of the statement below.
\begin{quote} Let $x$ and $y$ be real numbers. If $5x + 20y=754,$ then either $x$ or $y$ is not an integer. \end{quote}
\newpage
\item (20 points) Let $A$ and $B$ be sets. Prove that $A \subseteq B$ if and only if $\mathcal{P}(A) \subseteq \mathcal{P}(B).$
\newpage
\item (15 points) Let $A$, $B$, and $C$ be sets. If $A \subseteq B,$ then $C-B \subseteq C-A.$
\newpage
\item (20 points) Let $a,b,$ and $c$ be positive integers. Prove that if $c \mid a$ and $c \mid b,$ then $c \mid \gcd(a,b).$
\newpage
\end{enumerate}
\end{document}