\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}


% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
\usepackage{soul}

\newcommand{\blankbox}[2]{\fbox{\rule{#1}{0in}\rule{0in}{#2}}}
%special commands for number sets
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
%special commands for formatting: center, enumerate, pmatrix, vector span
\def\bc{\begin{center}}
\def\ec{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\spn}[1]{\text{Span}\left\{#1\right\}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\llra}{\longleftrightarrow}
\newcommand{\sse}{\subseteq}

\setlength{\headheight}{30pt}
\setlength{\headsep}{20pt}
\setlength{\fboxsep}{8pt}
\setlength{\fboxrule}{1pt}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

%header
\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 265: Exam 3 Review}}
\rhead{\large\sf\textbf{Spring 2026}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}
\begin{document}
\thispagestyle{fancy}

Exam 3 will be on Friday 3 April during our regular class time. It will include Chapters 9, 10, 11, and Section 12.1.  You will have one hour to complete the exam. You may bring a single 3 in by 5 in notecard with writing on both sides.\\

\begin{center} Definitions \end{center}

For all of the terms below, you must be able to formally state and use the definition from your textbook. 
\be
\item odd, even, same parity, opposite parity
\item divides, multiple, divisor
\item prime
\item greatest common divisor, least common multiple
\item congruent modulo $n$
\item rational number, irrational number
\item subsets, set equality
\item \textbf{relation on $A$, reflexive, symmetric, transitive relations, a relation from $A$ to $B$, an equivalence relation, an equivalence class, a partition of a set}
\item \textbf{a function from $A$ to $B$, domain, codomain, range of $f$}
\ee

\begin{center} Proof Techniques \end{center}
\be
\item direct proof
\item using cases
\item by contrapositive
\item by contradiction
\item if-and-only-if proofs
\item existence statements
\item \textbf{proofs involving sets (that is, statements including $A \subseteq B$ or $A=B$)}
\item \textbf{methods of disproving statements}
\item \textbf{proof by induction (both strong and weak)}
\ee

\newpage
\begin{center} Things to Keep in Mind \end{center}
\be
\item If a proof technique is not prescribed, you must state the method you are using.
\item You should put in the ``boiler-plate'' language even if you cannot figure out the whole proof.
\item You should expect to \emph{use} all of the hypotheses.
\item I will \emph{not} ask you to prove something that is false.
\ee

\begin{center} What the Midterm Will Look Like \end{center}
\be
\item Problem 1 (a) What is the standard way to show $X \subseteq Y$ for sets $X$ and $Y$? Your answer should be `` Pick an arbitrary element of the set $X$ and prove that it is in the set $Y.$
\item Problem 1 (b) Prove the proposition below using the standard method described above.  Proposition: If P, then $X \subseteq Y.$ (Clearly, P, X, and Y are specific.)
\item Problems 2 and Problems 3: Proofs by Induction.
\item Problem 4 about disproof.
\item Problem 5 about equivalence relations.
\ee
\end{document}