\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}


% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
\usepackage{soul}

\newcommand{\blankbox}[2]{\fbox{\rule{#1}{0in}\rule{0in}{#2}}}
%special commands for number sets
\def\R{{\mathbb R}}
\def\N{{\mathbb N}}
\def\Z{{\mathbb Z}}
\def\Q{{\mathbb Q}}
\def\C{{\mathbb C}}
%special commands for formatting: center, enumerate, pmatrix, vector span
\def\bc{\begin{center}}
\def\ec{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\spn}[1]{\text{Span}\left\{#1\right\}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\llra}{\longleftrightarrow}
\newcommand{\sse}{\subseteq}

\setlength{\headheight}{30pt}
\setlength{\headsep}{20pt}
\setlength{\fboxsep}{8pt}
\setlength{\fboxrule}{1pt}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

%header
\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 265: Exam 4 Review}}
\rhead{\large\sf\textbf{Spring 2026}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}
\begin{document}
\thispagestyle{fancy}

Exam 4 will be on Friday 24 April during our regular class time. It will include Chapter 12 and Chapter 14 Sections 1-2.  You will have one hour to complete the exam. You may bring a single 3 in by 5 in notecard with writing on both sides.\\

This review only discusses new material. However, you are expected to know all of the terms and proof techniques from the whole semester.\\

\begin{center} Definitions \end{center}

For all of the terms below, you must be able to formally state and use the definition from your textbook. 

\be
\item function, domain, codomain, range
\item injective (or one-to-one), surjective (or onto), bijective
\item composition of functions
\item inverse relations (or functions)
\item image, preimage, and associated notation
\item cardinality, countably infinite, countable, uncountable
\ee

\begin{center} Facts To Know \end{center}
\be
\item Pigeonhole principle
\item $|\N|=|\Z|=|\Q| \neq |\R|$
\item A set is countably infinite if and only if the elements of A can be written as an infinite sequence.
\item If $A$ and $B$ are countably infinite, then $A\cup B$ and $A \times B$ are countably infinite.
\ee


\begin{center} Things to Keep in Mind \end{center}
\be
\item If a proof technique is not prescribed, you must state the method you are using.
\item You should put in the ``boiler-plate'' language even if you cannot figure out the whole proof.
\item You should expect to \emph{use} all of the hypotheses.
\item I will \emph{not} ask you to prove something that is false.
\ee

\newpage
\begin{center} What the Midterm Will Look Like \end{center}
\be
\item Problem 1 (two parts): Prove a particular function is injective. Prove a particular function is surjective
\item Problem 2: Suppose $f:A \to B$ and $g:A \to B$. Prove that if $f$ and $g$ are injective (surjective), then $g \circ f$ is injective (surjective).
\item Problem 3: A Pigeonhole Principle problem
\item Problem 4: Prove that two sets have the same cardinality.
\item Problem 5: Short Answer which will come from questions like:
	\begin{itemize}
	\item Show a relation is (is not) a function
	\item Show a function is \emph{not} injective (surjective)
	\item Determine image/preimage of a set given a function and/or its inverse
	\item Demonstrating the mechanics of function composition
	\item Determine the inverse relation of a function
	\item Determine if a set is countable or uncountable
	\end{itemize}
\ee
\end{document}