\documentclass[12pt]{article}
\usepackage[margin=.8in]{geometry}
\usepackage{amsmath,amssymb,amsthm, latexsym, mathrsfs, pdfsync, 
fancybox, fancyhdr, 
graphicx, enumerate,
subfig, multicol}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{pgfplots}
\usetikzlibrary{calc}

\newcommand{\blankbox}[2]{\fbox{\rule{#1}{0in}\rule{0in}{#2}}}
%special commands for number sets
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
%special commands for formatting: center, enumerate, pmatrix, vector span
\def\bc{\begin{center}}
\def\ec{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\spn}[1]{\text{Span}\left\{#1\right\}}

\setlength{\headheight}{22pt}
\setlength{\headsep}{20pt}

\lhead{\sc Math 307\\ Discrete Math}
\chead{Quiz \#6\\ \S 3.3-3.5} 
\rhead{\sc Spring 2016}
\cfoot{}
\pagestyle{fancy}




\begin{document}
\thispagestyle{fancy}


\noindent {\Large{NAME:\underline{\hspace{3in}}}}\\

\noindent This quiz contains 3 problems worth 30 points. You may not use books, notes, or a calculator. You have 30 minutes to take the quiz.\\

\noindent \hrulefill
\be
%3.3\#20,21 like24-30
\item (12 points) Let $X=\{1,2,3,4,5\}$ and let $R$ be a relation on $X$ defined by the rule $(x,y) \in R$ if $x+y \leq 6.$
\be
\item List the elements of $R.$
\vfill
\item Is $R$ reflexive? Explain.
\vfill
\item Is $R$ symmetric? Explain.
\vfill
\item Is $R$ antisymmetric? Explain.
\vfill
\item Is $R$ transitive? Explain.
\vfill
\item Is $R$ a partial order? Explain.
\vfill
\item Is $R=R^{-1}$? Explain.
\vfill
\ee
\newpage
%#31
\item (10 points) Let $X=\{1,2,3,4,5,6,7,8,9,10\}$ and let  $R$ be a relation on $X \times X$ by $(a,b)R(c,d)$ if $a+d=b+c.$ Note that $R$ is an equivalence relation on $X \times X.$
\be
\item Give an example of two elements from $X \times X$ that relate to $(3,2).$
\vfill
\item Give an example of two elements for $X \times X$ that do \textbf{not} relate to $(3,2).$
\vfill
\item Show that $R$ is symmetric.
\vspace{1in}
\item List all members of the equivalence class $[ (8,1) ].$
\vfill
\ee
\item (8 points) 
\be
\item Write the matrix $A_1$ of the relation $R_1=\{(1,a),(2,a),(2,b),(3,c)\}$ with orderings: 1,2,3; a,b,c.
\vspace{1in}
\item Write the matrix $A_2$ of the relation $R_2=\{(a,y),(b,y),(b,z),(c,z)\}$ with orderings: a,b,c;x,y,z.
\vspace{1in}
\item List the ordered pairs in the relation $R_2 \circ R_1.$
\vfill
\item (2pts Extra Credit) Find the matrix product $A_1A_2$ and explain what its entries tell you about the relation $R_2 \circ R_1.$
\vspace{1in}
\ee
\ee
\end{document}