\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom,tabularx} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array}
\usepackage{pgf,tikz}
\usepackage{mathrsfs}

\usepackage[parfill]{parskip}
\usetikzlibrary{arrows}

\usetikzlibrary{calc}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=blue,only marks,mark=*}} \pgfplotsset{holdot/.style={color=blue,fill=white,only marks,mark=*}}

\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\renewcommand{\d}{\displaystyle}

\newcommand{\ans}[1][2]{ \ \rule{#1 in}{.5 pt} \ }


\pagestyle{fancy} 
%\lfoot{Uses a calculator}
\rfoot{4-7 (day 1)}

\begin{document}

\vspace*{-0.7in}

\begin{center}
  \Large\sc{Section 4.7 Optimization (Day 1)}\\
\end{center}
\begin{enumerate}
\item A Framework for Approaching Optimization
\begin{enumerate}
\item \textbf{Identify} the quantity to be minimized or maximized.
\item Chose \textbf{notation} and explain what it means.
\item Write the thing you want to maximize or minimize \textbf{as a function of one variable}, including a reasonable \textbf{domain}.
\item Use \textbf{calculus} to answer the question and \textbf{justify} that your answer is correct.
\end{enumerate}
Read the problem two or three times. Draw pictures. Label them. Pick specific numerical examples, to make the problem concrete. Be creative. Try more than just one approach. Organization matters.
\item  Find two positive numbers whose sum is 123 and whose product is a maximum.
\vfill
\newpage
\item A rancher has 1255 feet of fencing with which to
  enclose three adjacent rectangular corrals. See figure below. What dimensions should
  be used so that the enclosed area will be a maximum?\\
  
  \begin{tikzpicture}
  \draw[ultra thick] (0,0) -- (5,0) -- (5,3.5) -- (0,3.5) -- (0,0);
  \draw[ultra thick] (1,0)--(1,3.5) (3.2,0)--(3.2,3.5);
  \end{tikzpicture}
\vfill
   
\end{enumerate}
\end{document}
