\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
\lfoot{UAF Calculus 1}
\rfoot{first day }

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
  \large \sc{First Day of Class}
\end{center}


\begin{enumerate}
\item My teacher's name: Jill Faudree or Julie McIntyre\\ 
office: in Chapman (1 or 2 floors up!)\\ 
email:  jrfaudree@alaska.edu or jpmcintyre@alaska.edu\
\item Where can I get information about this class?\\
\begin{itemize}
\item by attending class
\item from the course webpage: \textit{https://uaf-math251.github.io/} \\(or just google: Calculus I at UAF)
\item from Canvas
\end{itemize}

\vfill
\item Where is my textbook?\\
\begin{itemize}
\item Our text -- OpenStax Calculus Volume 1, authors Herman \& Strang -- is available free online. \\
(google \emph{openstax calculus I})
\item Linked from the webpage and in Canvas
\item Note that it is possible to buy a hard copy. 
\end{itemize}
\vfill
\item How will I know what to expect in class?\\
On the webpage is a day by day schedule. It tells you what is happening in class every day. It gives the dates of all assessments including homework due dates, midterm dates, etc. 
\vfill
\item How will I be graded in this course? \\
Based on attendance, homework completion, quizzes and their corrections, and some tests
\vfill
\item Is there any extra credit in this class or any free points?\\
Yes. 
Free points for attending and participating in class. Free points for turning in your homework. Free points for correcting your quizzes.
Typically, midterms have extra credit problems that are designed to be just regular problems not extra hard problems.
\vfill
\item What will I need to do this week for this class?\\
\begin{itemize}
\item Participate in class every day. 
\item Sign up for a time to take a proctored ALEKS assessment no later than Friday.
\item Get started on Homework 1 (Review material).
\end{itemize}
\vfill

\item What should I do if I miss class?\\
Contact your instructor and let them know if the absence is excused.\\
Make time to learn the material of the day by reading the book, watching a video, going over the sheet of the day, getting started on the homework.
\vfill

\item What if I miss class on a quiz/midterm/final exam day?\\
Contact your instructor immediately. Explain why you missed class. 
\vfill

\item Is the homework online or written down? Where do I find it? How do I turn it in?\\
The homework is written. The problems can be found at the Course Webpage. You turn it in electronically using Gradescope which you access from Canvas.
\vfill
\item Will I have answers or solutions to the homework? Where are they?\\
Yes. Complete solutions are on Canvas. Look in the \emph{Assessments} tab.
\vfill
\item Does this mean I can just copy the solutions, upload them to Canvas and get full credit? \\
Yes. 
It should be clear that this is a very bad long-term strategy. 
\vfill
\item Where are my grades?\\
Grades live in Canvas.
\vfill

\item Where is the Math Lab?\\
Chapman 305, upstairs. Notably on the same floor as Jill's office. Note that Julie, Jill and our TA's will have weekly hours in the math lab!
\vfill
\item How will my teacher contact me? \\
In class. Canvas. Email.
\vfill
\item List the names of three people sitting next to you and give your name to them.
\vfill
\item What are the habits \emph{you} would like to adopt this semester in this class?\\
Get to class on time every day? Start the homework no later than the day the topic is covered? Schedule Calculus study time into your weekly schedule? Form a study group?
\end{enumerate}
\end{document}