\documentclass[12pt]{article}

% Layout.
\usepackage[top=1.2in, bottom=0.9in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=1.0]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Syllabus for MATH F314 Fall 2022 (Faudree)},
    pdfpagemode=FullScreen,
    }

\def\mailto#1{\href{mailto:#1}{#1}}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

\usepackage{fancyhdr}
\pagestyle{fancy} 
%\chead{\large\sf\textbf{}}
\lhead{\large\sf\textbf{Syllabus}}
\rhead{\large\sf\textbf{MATH F314 Linear Algebra, Fall 2022}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1} \smallskip\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}

\newenvironment{clist}%
{\bgroup\parskip 0pt\begin{list}{$\bullet$}{\partopsep 4pt\topsep 0pt\itemsep -2pt}}%
{\end{list}\egroup}%

\begin{document}

\strut\par\vskip-12pt
\heading{Essential Information}

\vskip -12pt
\strut\hbox to \hsize{\tableindent\vtop{\halign{#\hfill\ts&#\hfil\cr
{\emph{Instructor}} & Jill Faudree \quad \href{mailto:jrfaudree@alaska.edu}{\texttt{jrfaudree\@@alaska.edu}} \cr
\strut & \cr
{\emph{Course website}} & \href{https://jrfaudree.github.io/M314f2022/home.html}{\texttt{https://jrfaudree.github.io/M314f2022/home.html}}\cr
\strut & \cr
{\emph{Canvas site}} & \href{https://canvas.alaska.edu/}{\texttt{https://canvas.alaska.edu/}} \cr
\strut & \cr
\emph{Prerequisite} & MATH F252X Calculus II.\cr
\strut & \cr
{\emph{Basic Text}} & G.~Hefferon, \textit{Linear Algebra}, 4th Edition, Orthogonal Publishing, 2020 \cr
 &\href{https://hefferon.net/linearalgebra/}{\texttt{webpage for text}}\cr
  &\href{https://joshua.smcvt.edu/linearalgebra/book.pdf}{\texttt{free online textbook}}\cr
  &\href{https://joshua.smcvt.edu/linearalgebra/jhanswer.pdf}{\texttt{free online solutions manual}}\cr
  &\href{https://www.youtube.com/playlist?list=PLwF3A0R8OzMoMlE1-SaEh8h9VqUlO-r52}{\texttt{author videos}}\cr
}
\hfil}}

\heading{Description, Course Goals \& Student Learning Outcomes}

\emph{Catalog Description:} Linear equations, finite dimensional vector spaces, matrices, determinants, linear transformations and characteristic values. Inner product spaces.\\

Linear algebra is the branch of mathematics which covers vectors, matrices, and linear equations.  It is central to all areas of applied and pure mathematics because vectors are one way to describe complicated things by using many numbers.  Linear algebra is used in science and engineering, when modeling natural phenomena and computing efficiently using models.  Even nonlinear systems are approximated at first-order, using derivatives, by linear algebraic objects.

By the end of the course you will have a solid understanding of the fundamental concepts and algorithms of linear algebra, including well-known theorems and matrix factorizations.  You will have seen significant applications in diverse fields. You will be well-equipped to use linear algebra in more-advanced mathematics, and to use vectors and matrices in science and/or engineering.


\heading{Schedule and Online Materials}
The \href{https://jrfaudree.github.io/M314f2022/home.html}{course website} contains a embedded schedule listing the textbook sections to be covered each class, the dates each Homework is due, plus the dates for the Midterm Exams and the Final Exam.  You should consult this schedule frequently.  I will announce any Schedule adjustments in class.

Most course materials (Syllabus, Homework assignments, etc.) will be posted on the \href{https://jrfaudree.github.io/M314f2022/home.html}{course webpage}.  Some course materials (grades, announcements, etc.) will be available on the \href{https://canvas.alaska.edu}{Canvas site}.  Each website links to the other.


\heading{Class Time}
There are three hours of class meetings with your instructor every week: MWF 11:45 am -- 12:45 pm  Gruening 412.  You are expected to attend class and to participate.  Exams (below) and worksheets, including group activities, will occur in-class.


%\clearpage\newpage
%\phantom{foo}

\heading{Office Hours and Communication}
My Office Hours are online \href{https://docs.google.com/spreadsheets/d/e/2PACX-1vQ76z4RI6jhESlbN8vvxmtcY1rqmVvdfQmD433K4WA0a4Kyn_7lcYq68mq9tO0swUYd54hZedaHQuSP/pubhtml?gid=0&single=true}{\texttt{here}}.  Students can also schedule meetings with me outside of regular office hours.  I will use Canvas to send announcements.  If I need to contact you outside of class times, I'll try to email via Canvas.  Please set the email address in Canvas to one that you check regularly!


\heading{Evaluation and Grades}
Grades are determined as follows.  (Each component of the grade is discussed below.)

\begin{multicols}{2}
\begin{tabular}{|r|c|}
\hline
Class Participation& 5\%\\ \hline
Homework & 10\% \\  \hline
Quizzes & 15\%\\
\hline
Midterm Exam 1: Mon 10/10, in-class & 20\% \\
\hline
Midterm Exam 2: Mon 11/21, in-class & 20\%  \\
\hline
Final Exam: & 30\% \\
{Friday 12/16} 10:15am-12:15pm&\\
\hline
total & 100\% \, \\
\hline
\end{tabular}

\begin{tabular}{llll}
A  & 93--100\%& C  & 68--75\%  \\
A- & 90--92\% & C- & not given \\
B+ & 87--89\% & D+ & 65--67\%  \\
B  & 82--86\% & D  & 60--65\%  \\
B- & 79--81\% & D- & 57--59\%  \\
C+ & 76--78\% & F  & $\le$ 56\%
\end{tabular}
\end{multicols}

\vspace{-3mm}
These ranges are a guarantee and a lower bound. I reserve the right to increase your grade above these ranges based on the actual difficulty of the work and/or on average class performance. Any such increases will preserve grade ordering by weighted total score. 

\heading{Class Participation}
Many studies have demonstrated that attending class and being active in class are highly correlated with improved outcomes as measure by course grades and knowledge acquisition. In order to incentivize this behavior, it is rewarded as a part of your grade. 

Class participation includes not only being present in class but being an active participant in group activities.

\heading{Homework}
The weekly Homework assignments will include a selection of problems from the textbook, plus problems I have written.  Each Homework assignment should be turned in as a PDF via Gradescope, accessed via Canvas.  Assignments are due by 11:59pm on the dates stated on the \href{https://docs.google.com/spreadsheets/d/e/2PACX-1vS6mzghqdySBSt77fxeCwG3dFzjLlvvRVqtKPjE4XMysFBkQNuvpe4MO352YQRqhwnX032A4vdcT0w-/pubhtml}{Schedule}.  

Complete worked solutions to all textbook homework problems are already available online at the author's website. Thus, Homework will be graded for \emph{completion}.  

Problems very similar to the Homework problems will appear on the in-class Exams.

\heading{Quizzes}
We will have weekly in-class quizzes. These will consist of a selection of problems that are just like the homework and are an excellent way to determine if you have grasped the ideas of the previous week. We will go over these in class.

\heading{Exams}
There are two Midterm Exams this semester tentatively scheduled for Monday Oct 10 and Monday Nov 21.  Midterms are given during the class time.  Make-up Midterms will be given only for documented extenuating circumstances, at my discretion.

The cumulative Final Exam will be Friday December 16 10:15am-12:12pm.

\heading{Tutoring and Resources}
The Math and Stat Lab, Chapman Building Room 305, offers tutors.  For schedules and availability see \href{http://www.uaf.edu/dms/mathlab/}{\texttt{www.uaf.edu/dms/mathlab/}}.

Free one-on-one (or small group) tutoring is available in Chapman Room 201. You must schedule an appointment; see \href{http://www.uaf.edu/dms/mathlab/}{\texttt{www.uaf.edu/dms/mathlab/}}.

\heading{Rules and Policies}
\vskip -20pt

\subheading{Incomplete Grade} 
Incomplete (I) will only be given in
  DMS courses in cases where
  the student has completed the majority (normally all but the last
  three weeks) of a course with a grade of C or better, but for
  personal reasons beyond his/her control has been unable to complete
  the course during the regular term. Negligence or indifference are
  not acceptable reasons for granting an incomplete grade.

\subheading{Late Withdrawals} 
A withdrawal after the deadline from a DMS course will
  normally be granted only in cases where the student is performing
  satisfactorily (i.e., C or better) in a course, but has exceptional
  reasons, beyond his/her control, for being unable to complete the
  course.  These exceptional reasons should be detailed in writing to
  the instructor, Department Chair and the Dean.

\subheading{No Early Final Examinations}
Final examinations for DMS
  courses shall not be held earlier than the date and time published
  in the official term schedule. Normally, a student will not be
  allowed to take a final exam early. Exceptions can be made by
  individual instructors, but should only be allowed in exceptional
  circumstances and in a manner which doesn't endanger the security of
  the exam.

\subheading{Academic Dishonesty}
Academic dishonesty, including cheating and plagiarism, will not
be tolerated.  It is a violation of the Student Code of Conduct
and will be punished according to UAF procedures.
 
\subheading{COVID-19 statement}
Students should keep up-to-date on the university's policies, practices, and mandates related to COVID-19 by regularly checking this website:

\href{https://sites.google.com/alaska.edu/coronavirus/uaf?authuser=0}{\texttt{sites.google.com/alaska.edu/coronavirus/uaf}}

Students are expected to adhere to the university's policies, practices, and mandates and are subject to disciplinary actions if they do not comply.

\subheading{Student protections statement}
UAF embraces and grows a culture of respect, diversity, inclusion, and caring. Students at this university are protected against sexual harassment and discrimination (Title IX). Faculty members are designated as responsible employees which means they are required to report sexual misconduct. For more information on your rights as a student and the resources available to you to resolve problems, please go to the following site:

\href{https://catalog.uaf.edu/academics-regulations/students-rights-responsibilities/}{\texttt{catalog.uaf.edu/academics-regulations/students-rights-responsibilities/}}

\subheading{Disability services statement}
I will work with the Office of Disability Services (\href{https://www.uaf.edu/disabilityservices/}{\texttt{www.uaf.edu/disabilityservices/}}) to provide reasonable accommodation to students with disabilities.

\subheading{Student Academic Support}

\vspace{-7mm}
\begin{itemize}
\item Speaking Center (907-474-5470, \mailto{uaf-speakingcenter@alaska.edu}, Gruening 507)
\item Writing Center (907-474-5314, \mailto{uaf-writing-center@alaska.edu}, Gruening 8th floor)
\item UAF Math Services, Chapman 210 (\href{http://www.uaf.edu/dms/mathlab/}{\texttt{www.uaf.edu/dms/mathlab/}})
\item Developmental Math Lab, Gruening 406
\item The Debbie Moses Learning Center at CTC (907-455-2860, 604 Barnette St, Room 120, (\href{https://www.ctc.uaf.edu/student-services/student-success-center/}{\texttt{ctc.uaf.edu/student-services/student-success-center/}})
\item For more information and resources, please see the Academic Advising Center Student Resources list (\href{https://www.uaf.edu/advising/student-resources/}{\texttt{www.uaf.edu/advising/student-resources/}}).
\end{itemize}

\subheading{Student Resources}

\vspace{-7mm}
\begin{itemize}
\item Disability Services (907-474-5655, \mailto{uaf-disability-services@alaska.edu}, Whitaker 208)
\item Student Health \& Counseling [6 free counseling sessions] (907-474-7043, \href{https://www.uaf.edu/chc/}{\texttt{www.uaf.edu/chc/}}, Whitaker 203)
\item Center for Student Rights and Responsibilities (907-474-7317, \mailto{uaf-studentrights@alaska.edu}, Eielson 110)
\item Associated Students of the University of Alaska Fairbanks (ASUAF) or ASUAF Student Government (907-474-7355, \mailto{asuaf.office@alaska.edu}, Wood Center 119)
\end{itemize}

\subheading{Nondiscrimination statement}
The University of Alaska is an affirmative action/equal opportunity employer and educational institution. The University of Alaska does not discriminate on the basis of race, religion, color, national origin, citizenship, age, sex, physical or mental disability, status as a protected veteran, marital status, changes in marital status, pregnancy, childbirth or related medical conditions, parenthood, sexual orientation, gender identity, political affiliation or belief, genetic information, or other legally protected status. The University's commitment to nondiscrimination, including against sex discrimination, applies to students, employees, and applicants for admission and employment. Contact information, applicable laws, and complaint procedures are included on UA's statement of nondiscrimination available at www.alaska.edu/nondiscrimination. For more information, contact:

\begin{tabular}{l}
UAF Department of Equity and Compliance\\
1760 Tanana Loop, 355 Duckering Building, Fairbanks, AK  99775\\
907-474-7300 \quad \mailto{uaf-deo@alaska.edu}
\end{tabular}

\hfill  \scriptsize [syllabus version: \today] \normalsize

\end{document}
