
\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=black,only marks,mark=*}} \pgfplotsset{holdot/.style={color=black,fill=white,only marks,mark=*}}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal }}


\pagestyle{fancy} 
\lfoot{}
\rfoot{3-3 Derivative Rules}

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\renewcommand{\d}{\displaystyle}

\vspace*{-0.7in}

%%%%%%%%%intro page
\begin{center}
  \large
  \sc{Section 3-3: Derivative Rules (day 2)}\\
\end{center}
Read Section 3.3. Work the embedded problems. \\
\begin{enumerate}
\item Review (aka mini-quiz)\\
	\begin{enumerate}
	\item Fill in the following rules -- from memory if possible!\\
	\begin{multicols}{2}
	\begin{enumerate}
	\item $\displaystyle{\frac{d}{dx}\left[f(x)\: g(x)\right]=}$\\

	\item $\displaystyle{\frac{d}{dx}\left[\frac{f(x)}{g(x)}\right]=}$\\

	\end{enumerate}
	\end{multicols}
	
	\item Find the derivative of each of the following. Use whatever rule you choose. Simplify if you have time.
	\begin{enumerate}
	\item $H(x)=\frac{1}{3x}(8+x^2)$
	\vfill
	\item $G(x)=\frac{3x}{8+ x^2}$
	\vfill
	\end{enumerate}
	\end{enumerate}
\item Determine the point (or points) where the graph $f(x)=x^3$ has a slope of 2. Write the equation of the tangent line at this point (or points). On the same axes, sketch $f(x)$ and the tangent line(s).
\vfill

\newpage
\item The concentration of an antibiotic in the bloodstream $t$ hours after being injected is given by $\displaystyle{C(t)=\frac{2t^2+t}{t^3+50}}$ where $C$ is measured in milligrams per liter of blood.	
	\begin{enumerate} 
	\item Find $C(0)$ and $C(10)$ and explain (in complete sentences,  including units) what these numbers mean in the context of the problem. \\
	\vfill
	\item Find $C'(t)$. (Yes. This will be challenging/painful. I put the simplified answer at the bottom of this page so you can check your answer!)
	\vfill
	
	\item It is the case that $C'(0)=0.02$ and $C'(10)=-0.018.$ Explain (in a complete sentence or sentences) what these numbers mean. \textbf{Include units.}\\
	\vfill
	
	\item Briefly describe what seems to be occurring as the number of hours increases.
	\vfill
	\end{enumerate}
\item An ant walking along a sidewalk has traveled $s(t)=t^4-2t^2$ inches in $t$ minutes.  Find the acceleration of the ant (with units) when the velocity of the ant is 0.
\vfill
\item Bonus Problem: Find the point on the graph of $f(x)=x^3$  such that the tangent line at that point has an $y$ intercept of 6.

\hfill {\small{$C'(t)=\frac{-2(t^4+t^3-100t-25)}{(t^3+50)^2}$}}

\end{enumerate}
\end{document}

