\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace, adjustbox}
\usepackage{array%,tikz, pgfplots
}

\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}
%
\pagestyle{fancy} 
\lfoot{UAF Calculus I}
\rfoot{4-1}


\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\begin{document}
\setlength{\parindent}{0cm}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
 {\large{ \sc{Section 4-1: Related Rates}}}
\end{center}
 	
A strategy.
\begin{itemize}
\item Draw a \fbox{picture}.
\item Identify what you \fbox{want} and what you \fbox{know} 
\item \fbox{Take derivative with respect to $t.$} 
\item \fbox{Solve} for what you \fbox{want}.
\end{itemize}

\hrulefill

\begin{enumerate}
\item  Water runs into a conical tank at the rate of 9
ft$^3$/min. The tank stands point down and has a height of 10 ft and a
base radius of 5 ft. How fast is the water level rising when the water
is 6 ft deep?  
\vfill
\newpage
\item  A street light is mounted at the top of a
10-ft-tall pole. A woman 5 ft tall walks away from the pole along a
straight path at a speed of 5 ft/s. How fast is the tip of her shadow moving when she is 40 ft from the pole?
\vfill

\item  A hot air balloon rising straight up from a level
field is tracked by a range finder 500 feet from the lift-off
point. At the moment the range finder's elevation angle is $\pi/4$,
the angle is increasing at the rate of 0.14 radians/min. How fast is
the balloon rising at that moment? 
\vfill
\end{enumerate}
\end{document}