\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace, adjustbox}
\usepackage{array%,tikz, pgfplots
}

\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal }}
%
\pagestyle{fancy} 
\lfoot{UAF Calculus I}
\rfoot{4-5}


\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\begin{document}
\setlength{\parindent}{0cm}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
 {\large{ \sc{Section 4.5: Derivatives and the Shape of the Graph (day 2)}}}
\end{center}
 \begin{enumerate}
 \item The Second Derivative Test
 \vspace{2in}
\item Use the Second Derivative Test to find the local extrema for $f(x)=-3x^5+5x^3.$
\vspace{1in}
 \item For the function $f(x)=\sqrt[3]{x}(1-x)$, determine (a) intervals where $f$ is increasing/decreasing, (b) the locations of any local extrema (c) intervals where $f$ is concave up / concave down (d) inflection points. Then use technology to confirm your answers.
 \newpage
 \item  Below is the graph of the \emph{derivative} of $f$, \large{$f'(x)$}. Use this graph to answer the questions.
 
 \begin{multicols}{2}
\begin{tikzpicture}
\begin{axis}[scale=1, thick, my style, xtick={-4,-2,...,4}, ytick={-4,-2,...,4},
xmin=-4.5, xmax=4.5, ymin=-4.5, ymax=4.5, minor y tick num=1,
        minor x tick num=1, mark size=3.0pt, grid=both, grid style={ thin, black!60, dashed}, axis equal image]
%%Curve
\addplot[ultra thick, smooth,<->] coordinates {(-4,4) (-3,0) (-2,-2) (-1,0) (0,1) (2,0) (3,1) (4,4)};
\end{axis}
\end{tikzpicture}
\quad

\vspace{.3in}
\quad

\columnbreak

\begin{enumerate}
\item On what intervals is $f(x)$ increasing? decreasing?
\vfill
\item Determine the location of local extrema of $f$.
\vfill
\item On what intervals is $f(x)$ concave up? concave down?
\vfill
\item Determine the location of any inflection points of $f$.
\vfill
\end{enumerate}
\end{multicols}
\vfill
\item Sketch a graph that satisfies \emph{all} of the properties below.
\begin{enumerate}
\item $f(2)=f(4)=0$
\item $f'(x) > 0$ if $x <3$
\item $f'(3)$ does not exist
\item $f'(x) < 0$ if $x > 3$
\item $f''(x) > 0$ for $x \not=3.$
\end{enumerate}
\vspace{2.5in}
 \end{enumerate}
\end{document}