\documentclass[12pt]{article}
\usepackage[margin=.8in]{geometry}
\usepackage{amsmath,amssymb,amsthm, latexsym, mathrsfs, pdfsync, 
fancybox, fancyhdr, 
graphicx, enumerate,
subfig, multicol}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{pgfplots}
\usetikzlibrary{calc}

\newcommand{\blankbox}[2]{\fbox{\rule{#1}{0in}\rule{0in}{#2}}}
%special commands for number sets
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
%special commands for formatting: center, enumerate, pmatrix, vector span
\def\bc{\begin{center}}
\def\ec{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bv}[1]{\mathbf{#1}}
\newcommand{\spn}[1]{\text{Span}\left\{#1\right\}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\llra}{\longleftrightarrow}

\setlength{\headheight}{30pt}
\setlength{\headsep}{20pt}
\setlength{\fboxsep}{8pt}
\setlength{\fboxrule}{1pt}

\lhead{\sc Math 307\\ Discrete Math}
\chead{\sc Worksheet \S 6.2} 
\rhead{\sc Spring 2016 \\1 April 2016}
\cfoot{}
\pagestyle{fancy}
\pgfplotsset{compat=1.12}
\begin{document}
\thispagestyle{fancy}

\quad
Name: \\

\quad
\bc Section 6.2 \ec

Assume there is a club with 7 girls and 8 boys.
\be
\item In how many ways can the members line up for a photograph?
\vfill
\item In how many ways can a President, Vice-President, Secretary and Treasurer be elected assume no one holds more than one position?
\vfill
\item In how many ways can P, VP, S and T be elected such that girl 1 is P or boy 1 is VP?
\vfill
\item In how many ways can the club form a committee of 5 people?
\vfill
\newpage
\item In how many ways can the club form a committee of 2 girls and 2 boys?
\vfill
\item In how many ways can the club from a committee of 4 people that contains at least one boy?
\vfill
\item In how many ways can the club from a committee of 4 people that contains at most one boy?
\vfill
\item In how many ways can the club form a committee of 4 people that contains at least one boy and at least one girl?
\vfill
\item In how many ways can the club form a committee of 4 people such that boy 1 and boy 2 do not have to serve together?
\vfill
\ee

\end{document}

