\documentclass[11pt]{article}
\usepackage[margin=1in, head=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatim}

%\usepackage{pdfsync}
\addtolength{\textwidth}{.5in}
\addtolength{\leftmargin}{-1in}
\addtolength{\textheight}{.5in}
\addtolength{\topmargin}{-0.5in}

%\pagestyle{fancy}
%\lhead{MATH 200X }
%\chead{Fall 2007}
%\rhead{FINAL EXAM}
%\lfoot{}
%\cfoot{\thepage}
%\rfoot{}

\setcounter{secnumdepth}{0}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\clm}{\par\textit{Claim:}\par}
\newcommand{\diam}{\mathrm{diam}}
\newcommand{\sect}{\textsection}

\parindent=0in
\parskip=0.5\baselineskip

\begin{document}
\newgeometry{top=3in}
\begin{center}
\vspace{2in}

\huge{Math 156 PRECALCULUS \\
Fall 2015}

\vfill

\huge{\bf{Quiz 6 -- Version One}}\\

\vspace{0.5in}

\large{Thursday, October 22, 2015}\\

\vfill


{\huge{Name:{\underline{\hspace{2in}}}}}
\vfill
This quiz has 6 problems worth a total of 30 points. It is TWO SIDED. 
\vfill
\end{center}
\newpage
\restoregeometry
\begin{enumerate}
%3.2 #15-30
\item (5 points) For $P(x)=\frac{-1}{6}(x+2)(x-1)^2(x-3).$ Sketch the graph of $P(x).$ Label any $x$- or $y$-intercepts and exhibit the proper end behavior.
\vspace{2in}
\vfill
%3.3#15-24
\item (4 points) Find the quotient, $Q(x),$ and remainder, $R(x),$ of $\frac{x^4+4x^3-8x^2+15}{x^2-3}$ using long division. {\bf{Make sure you identify them!}}
\vfill
\newpage
%3.1 #9-24
\item (5 points) Let $f(x)=5x^2+2x-1.$
\begin{enumerate}
\item Express $f$ in standard form.
\vspace{1.5in}
\item Find the vertex of $f.$
\vspace{0.5in}
\end{enumerate}
%3.1 #9-24
\item (6 points) Given $f(x)=-4(x+5)^2+9,$ a quadratic function in standard form, answer the questions below.
\begin{enumerate}
\item Find the $y$-intercept(s) of $f,$ or state that none exist.
\vfill
\item Find the $x$-intercept(s) of $f,$ or state that none exist.
\vfill
\item Find the range of $f(x).$
\vfill
\end{enumerate}
\newpage

%3.6 \#31-62
\item (6 points) Let $g(x)=\frac{8x^3}{x^3+6x^2+8x}.$
\begin{enumerate}
\item Find all horizontal asymptotes, if any exist.
\vfill
\item Find all vertical asymptotes, if any exist.
\vfill
\item Find all $y$-intercepts, if any exist.
\vfill
\end{enumerate}
%3.7 #17-36
\item (4 points) Solve the inequality $\frac{x-3}{2x+5}\geq 1.$
\vspace{3in}
\end{enumerate}
\end{document}
