% !TEX TS-program = pdflatexmk
\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}\headsep = 0.2 in
%\parskip = 0.2in
%\parindent = 0.0in

\usepackage{amsmath,amssymb,latexsym,graphicx,amsthm,enumerate}
\usepackage{palatino, url, multicol,tikz}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{axiom}{Axiom}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{exercise}{Exercise}%[section]
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
\def\bc{\begin{center}}
\def\ec{\end{center}}
\def\be{\begin{enumerate}}
\def\ee{\end{enumerate}}
\def\bi{\begin{itemize}}
\def\ei{\end{itemize}}
\def\bs{\begin{slide}}
\def\es{\end{slide}}
%\def\bx{\begin{exercise}}
\newcommand{\bx}[1]{\begin{exercise}({#1} pts.)}
\def\ex{\end{exercise}}
\def\t{\times}
%\def\[{\left[}
%\def\]{\right]}
%\def\({\left(}
%\def\){\right)}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\oimp}[1]{\overset{#1}{\Longleftrightarrow}}
\newcommand{\bv}[1]{\ensuremath{ \mathbf{\vec{#1}}} }
\renewcommand{\d}{\displaystyle}
\newcommand{\bcd}{\boldsymbol{\cdot}}

\begin{document}
{\bf Math 253 Calculus III Fall 2018 \hfill Quiz \# 6,  17 October 2018 }\\
\\
{\bf Name: \rule{3.5in}{1pt}}\\
\\
\noindent There are 20 points possible on this quiz. This is a closed
book quiz and closed note quiz. Calculators are not allowed. If you have any questions, please
raise your hand.

\begin{enumerate}
%section 14.5
\item (4 points) Use the Chain Rule to find $\partial z / \partial t$ if $z=y^2\arctan(2x)$, $x=e^{st}$, $y=t^2 +s^3.$
\vfill
\item (6 points) The temperature at a point $(x,y)$ is $T(x,y)$, measured in degrees Celsius. A bug crawls so that its position after $t$ seconds is given by $x=3 \cos (2 \pi t)$, $y=4+\sqrt{t}$ where $x$ and $y$ are measured in centimeters. The temperature function satisfies  $T_x(3,5)=8$ and $T_y(3,5)=-6.$ 
\be
\item In the context of the problem (temperature, crawling bug), explain the meaning of $T_x(3,5)=8$ in language your parents could understand.
\vspace{1in} 
\item How fast is the temperature changing on the bug's path after 1 second? (Give units with your answer.)
\vfill
\ee
\newpage
\item (4 points) Find the equation of the tangent plane to the surface $x=y^2+z^2+1$ at the point $(14,2,3).$
\vfill
\item (6 points) Suppose that over a certain region of space the electrical potential $V$ is given by the following equation:
$$V(x,y,z)=xy^2+yz.$$
	\be
	\item Find the rate of change of the potential at the point $P(-1,2,4)$ in the direction of the vector $\textbf{v}=2\textbf{i}-2\textbf{j}+\textbf{k}.$
	\vfill
	\item In which direction does $V$ change most rapidly at $P$?
	\vfill
	\item What is the maximum rate of change of $V$ at $P$?
	\vfill
	\ee


\end{enumerate}
\end{document}