% !TEX TS-program = pdflatexmk
\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}\headsep = 0.2 in
%\parskip = 0.2in
%\parindent = 0.0in

\usepackage{amsmath,amssymb,latexsym,graphicx,amsthm,enumerate}
\usepackage{palatino, url, multicol}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{axiom}{Axiom}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{exercise}{Exercise}%[section]
\def\RR{{\mathbb R}}
\def\NN{{\mathbb N}}
\def\ZZ{{\mathbb Z}}
\def\QQ{{\mathbb Q}}
\def\CC{{\mathbb C}}
\def\bc{\begin{center}}
\def\ec{\end{center}}
\def\be{\begin{enumerate}}
\def\ee{\end{enumerate}}
\def\bi{\begin{itemize}}
\def\ei{\end{itemize}}
\def\bs{\begin{slide}}
\def\es{\end{slide}}
%\def\bx{\begin{exercise}}
\newcommand{\bx}[1]{\begin{exercise}({#1} pts.)}
\def\ex{\end{exercise}}
\def\t{\times}
%\def\[{\left[}
%\def\]{\right]}
%\def\({\left(}
%\def\){\right)}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\oimp}[1]{\overset{#1}{\Longleftrightarrow}}
\newcommand{\bv}[1]{\ensuremath{ \mathbf{\vec{#1}}} }
\renewcommand{\d}{\displaystyle}

\begin{document}
{\bf Math 253 Calculus III Fall 2018 \hfill Quiz \# 0,  28 Aug 2018 }\\
\\
{\bf Name: \rule{3.5in}{1pt}}\\
\\
\noindent There are 20 points possible on this quiz. This is a closed
book quiz and closed note quiz. Calculators are not allowed. If you have any questions, please
raise your hand.

\begin{enumerate}
\item Let $A(3,-2,4)$ and $B(1,2,5)$ be points in $\mathbb{R}^3.$
\begin{enumerate}
\item Find $|AB|,$ the distance between the points $A$ and $B.$
\vspace{0.75in}
\item Find the distance from point $A$ to the $xz$-plane.
\vspace{0.75in}
\item Find the distance from point $A$ to the $x$-axis.
\vspace{0.75in}
\end{enumerate}
\item 
\begin{enumerate}
\item Describe the surface in $\mathbb{R}^3$ represented by the equation $z=5.$ (You may provide a sketch if you like but you are not required to do so.)
\vfill
\item Describe the set of points $(x,y,z)$ in $\mathbb{R}^3$ such that $z=5$ and $x=1.$ Note, the set of points you describe must satisfy \emph{both} equations. (You may provide a sketch if you like but you are not required to do so.)
\vfill
\end{enumerate}
\newpage
\item 
\begin{enumerate}
\item Find the equation of the sphere with center $(-3,1,6)$ and radius 3.
\vfill
\item Describe the intersection of the sphere and the $xz$-plane.
\vfill
\item Describe the intersection of the sphere and the $yz$-plane.
\vfill

\end{enumerate}
\end{enumerate}
\end{document}
%Book probs 1.1
\item (2 points) Let $\:\mathcal{U}=\mathbb{Z}^+,$ $X=\{1,2,3,4,5\}$ and $Y=\{2n \: | \: n \in \mathbb{Z}^+ \}.$ For each set below, list the elements or use set builder notation to indicate the members of the set.
\begin{multicols}{2}
\begin{enumerate}
\item $X \cap Y$
\item $\overline{X} \cap \overline{Y}$
\end{enumerate}
\end{multicols}
\vspace{1in}

\item (2 points) In each problem below, determine if $A \subseteq B$ and justify your answer.
\begin{multicols}{2}
\begin{enumerate}
\item $A=\{3n \: | \: n \in \mathbb{Z}^+\}, \: B=\{2n \: | \: n \in \mathbb{Z}^+ \}$
\item $A=\{10, 20, 30 \}, \: B=\{2n \: | \: n \in \mathbb{Z}^+ \}$
\end{enumerate}
\end{multicols}
\vspace{1in}


%Similar probs 1.1
\item (1point) What is the cardinality of the set $A=\{\: 1, \:2, \: \{1,2\}, \: \emptyset, \:3,\: 4\:\}$?\\
%$B=\{\: a,  \{a,b\}, \{b,c,d,e\} \: \emptyset \}.$\\
%$C=\{\: 1, \: 3, \: 5, \: \{2,4,6\}, \emptyset \}.$

%Book problem 1.2
\item (1 point) A coin is flipped 10 times. Write the negation  of the proposition: \emph{Some heads and some tails were obtained.}\\
\vfill

%Similar problem 1.3
\item (2 points) Given the conditional proposition: \emph{P: \: If the marble is red, then the house is not blue.}
\begin{enumerate}
\item In words, write the negation of $P$
\vfill
\item In words, write the \emph{converse} of $P.$
\vfill 
\end{enumerate}
\newpage

%Book problem
\item (1 point) Determine the truth value of the proposition: If $3+5 < 2,$ then $1+3 \not=4.$\\

 %fill in the blank
 \item (4 points) Fill in the blanks below:
 \begin{enumerate}
 \item Let $A$ and $B$ be sets. De Morgan's Laws for sets say $\overline{A \cup B} =$ \underline{\hspace{1.5in}}.\\
 \item Let $p$ and $q$ be propositions. Then $p \rightarrow q \equiv$ \underline{\hspace{1.5in}} $\equiv$ \underline{\hspace{1.5in}}.\\
 \item Let $p$ and $q$ be propositions. Then De Morgan's Laws for Logic say $\neg(p \wedge q ) \equiv $ \underline{\hspace{1.5in}}.\\
 \end{enumerate}
 
%Problem 1.2 and 1.3
\item (3 points) Given $p$ and $q$ are true and $r$ is false, determine the truth value of the proposition below. Justify your answer.
$$ (p \rightarrow r) \: \leftrightarrow (q \wedge(\neg p \vee r))$$
\vspace{1in}

%problem 1.2 and 1.3
\item (4 points) Write a truth table for $ p \rightarrow \neg ( q \vee  p)$.
\vspace{3in}




\end{enumerate}
 \end{document}


 