
\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=black,only marks,mark=*}} \pgfplotsset{holdot/.style={color=black,fill=white,only marks,mark=*}}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$}, axis equal }}


\pagestyle{fancy} 
\lfoot{}
\rfoot{3-3 Derivative Rules (day 2)}

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\renewcommand{\d}{\displaystyle}

\vspace*{-0.7in}

%%%%%%%%%intro page
\begin{center}
  \large
  \sc{Section 3-3: Derivative Rules (day 2)}\\
\end{center}
\begin{enumerate}
\item Find the derivative of each of the following. Use whatever rule you choose. Simplify if you have time.
	\begin{enumerate}
	\item $G(x)=\frac{x^2}{8+ x^2}$
	\vfill
	\item $K(x)=\frac{8+ x^2}{x^2}$
	\vfill
	\item $H(x)=\frac{1}{3x}(8+x^2)$
	\vfill
	\item $f(x)=5e^2+4{x}^{3/4}+5x\sin(x)$\\
	\vfill
	\item $g(x)=\frac{2}{3}-\frac{2}{x}+\frac{x}{2}+ \frac{\cos(x)}{x+6}$\\
	\vfill
	\end{enumerate}
\newpage
\item Determine the point (or points) where the graph $f(x)=x^3$ has a slope of 2. 
\vfill

\item An ant walking along a sidewalk has traveled $s(t)=t^4-2t^2$ inches in $t$ minutes.  Find the acceleration of the ant (with units) when the velocity of the ant is 0.
\vfill

\item The concentration of an antibiotic in the bloodstream $t$ hours after being injected is given by $\displaystyle{C(t)=\frac{2t^2+t}{t^3+50}}$ where $C$ is measured in milligrams per liter of blood.	
	\begin{enumerate} 
	\item Find $C(0)$ and $C(10)$ and explain what these numbers mean in the context of the problem. \\
	\vspace{.5in}
	\item It is a fact that $C'(t)=\frac{-2(t^4+t^3-100t-25)}{(t^3+50)^2}.$ What are the units of $C'(x)$?
	\vspace{.5in}
	
	\item It is a fact that $C'(10)=-0.018.$ Interpret this fact in the context of the problem. Use language a Precalculus student could understand. \\
	\vspace{.5in}
	
	\item Use the fact from parts (a) and (c) to make a guess about $C(11).$
	\vspace{.5in}
	\end{enumerate}

\end{enumerate}
\end{document}

