\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom,tabularx} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array}
\usepackage{pgf,tikz}
\usepackage{mathrsfs}

\usepackage[parfill]{parskip}
\usetikzlibrary{arrows}

\usetikzlibrary{calc}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=blue,only marks,mark=*}} \pgfplotsset{holdot/.style={color=blue,fill=white,only marks,mark=*}}

\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\renewcommand{\d}{\displaystyle}

\newcommand{\ans}[1][2]{ \ \rule{#1 in}{.5 pt} \ }


\pagestyle{fancy} 
%\lfoot{Uses a calculator}
\rfoot{4-7 (day 2)}

\begin{document}

\vspace*{-0.7in}

\begin{center}
  \Large\sc{Section 4.7 Optimization (Day 2)}\\
\end{center}
\begin{enumerate}
\item A rectangular storage container with lid is to have a volume of 36 cubic inches. The length of the base is three times the width. Material for the base and lid costs \$4 per square inch. Material for the sides costs \$1 per square inch. Find the cost of materials for the least expensive container.
\vfill
\item Which points on the graph of $y = 4-x^2$ are
  closest to the point $(0, 2)$?\\
   HINT: Whenever you are asked to maximize or minimize distance, it is nearly ALWAYS easier to maximize or minimize the \emph{square} of the distance. Why?
\vfill
\newpage
\item Find the area of the largest rectangle that can
  be inscribed in a semicircle of radius $r$.\\ \textbf{Hint:} The radius $r$ of your circle can be considered a fixed constant. You will expect it to appear in your answer. 
  \vfill
\item An oil refinery is located on the north bank of a
straight river that is 2 km wide. A pipeline is to be constructed from
the refinery to storage tanks located on the south bank of the river 10
km downstream of the refinery. The cost of laying pipe is \$ 10,000/
km over land to a point $P$ on the opposite bank and then \$ 40,000/km
under the river to the tanks. To minimize the cost of pipeline, where
should $P$ be located? 
\vfill

\end{enumerate}
\end{document}
