\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
\lfoot{UAF Calculus 1}
\rfoot{first day }

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
  \large \sc{First Day of Class}
\end{center}


\begin{enumerate}
\item My teacher's name: \underline{Jill Faudree }\\ office:  \underline{Chapman Hall 306B}\\ email:  \underline{jrfaudree@alaska.edu}\\

\item Where can I get information about this class?\\
\begin{itemize}
\item by attending class and checking Jill's webpage just for this section: \\
	\url{https://jrfaudree.github.io/M251s2022/home.html}
\item from the course webpage: \url{https://uaf-math251.github.io/} \\(or just google: Calculus I at UAF)
\item from Canvas
\end{itemize}

\vfill
\item Where is my textbook?\\
\begin{itemize}
\item Our text -- OpenStax Calculus Volume 1, authors Herman \& Strang -- is available free online. \\
(google \emph{openstax calculus I})
\item general info can be found here: \textit{https://openstax.org/details/books/calculus-volume-1} 
\item Note that it is possible to buy a hard copy. 
\item There are student resources online including a free student solutions manual.
\end{itemize}
\vfill
\item Where will I go tomorrow?\\
Go to Chapman 106. After a brief intro, those with laptops will get started and those without will go across the hall to the computer lab.
\vfill
\item How will I be graded in this course? \\
Based on attendance, homework completion, quizzes and their corrections, and some tests
\vfill
\item What do I need to do in the next 24 hours for this class?\\
\begin{itemize}
\item Go to the Calculus I webpage and find (i) syllabus (ii) weekly schedule (iii) instructor info and (iv) the textbook.
\item Read through the whole syllabus.
\item Look at the Weekly Schedule. Focus on Week 1 and Week 2.
\item Make sure you have Canvas set up to notify you of class announcements.
\end{itemize}
\vfill
\item What will I need to do this week for this class?\\
\begin{itemize}
\item Attend class every day (MTWThF)
\item Bring your laptop to class tomorrow (Tuesday), if possible.
\item Complete a practice ALEKS assessment for extra credit no later than 11:59 PM Tuesday Jan 11.
\item Sign up for a 2 hour time-slot to take your proctored ALEKS PPL no later than Friday Jan 9.
\item Do 5 hours in learning mode or reach 90\% of your pie no later than 11:59 PM next Monday (Jan 17)
\end{itemize}
\vfill
\item What are the quizzes like?\\
They are based on the homework problems and things discussed in class. You have 30 minutes to complete them. You can correct your quiz in class for points back.
\vfill
\item Is the homework online or written down? Where do I find it? How do I turn it in?\\

The homework is written. The problems can be found at the Course Webpage. You turn it in electronically using Gradescope which you access from Canvas.
\vfill
\item Will I have answers or solutions to the homework? Where are they?\\

Yes. \\
Complete solutions are on Canvas.
\vfill
\item Does this mean I can just copy the homework from the solutions, upload them to Canvas and get full credit? \\

Yes. \\
It should be clear that this is a very bad long-term strategy. See the answer to question \#8.
\vfill



\item Where are my grades?\\
Grades live in Canvas.
\vfill

\item Where is the Math Lab?\\
Chapman 305. Notably on the same floor as Jill's office. Note that Jill and our TA's have weekly hours in the math lab!
\vfill

\item Where is the Chapman Computer Lab? The Rasmuson Computer Lab?\\
Chapman lab on the first floor right across the hall from our Tuesday/Thursday classroom.\\
The Rasmuson Lab is in Rasmuson Library. The third floor is down one level from ground level.
\vfill

\item How will my teacher contact me? \\
In class. Canvas. Email.
\vfill
\item List the names of three people sitting next to you and give your name to them.
\vfill
\end{enumerate}
\end{document}