\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace, adjustbox}
\usepackage{array%,tikz, pgfplots
}

\usepackage{tikz, pgfplots}
\usetikzlibrary{calc}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}
%spring 2020 file
\pagestyle{fancy} 
\lfoot{UAF Calculus I}
\rfoot{3-7 Rates of Change Applications}


\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\begin{document}
\setlength{\parindent}{0cm}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
\vspace*{-0.7in}
\begin{center}
 {\large{ \sc{Section 3.7 Rates of Change in the Natural and Social Sciences}}}
\end{center}
\begin{enumerate}
\item A particle moves according to the law of motion $s(t)=2-15t+4t^2-\frac{1}{3}t^3,$ for $t \geq 0$, where $t$ is measured in seconds and $s$ is measured in feet.
	\begin{enumerate}
	\item Find the velocity at time $t.$
	\vfill
	\item What is the velocity after 1 second?
	\vfill
	\item When is the particle at rest?
	\vfill
	\item When is the particle moving in the positive direction?
	\vfill
	\item Draw a diagram of the particle from $t=0$ to $t=6.$
	\vfill
	\item Find the \emph{displacement} of the particle during the first 6 seconds.
	\vfill
	\item Find the \emph{total distance traveled} by the particle during the first 6 seconds.
	\vfill
	\item Find the acceleration of the particle.
	\vfill
	\item Graph the acceleration function.
	\vfill
	\item When is the particle speeding up?
	\vfill
	\end{enumerate}
\newpage
\item The height (in meters) of a projectile shot vertically upward from a point 10 meters above ground lever with an initial velocity of 20 meters per second is $h=10+20t-4.9t^2.$
	\begin{enumerate}
	\item When does the projectile reach its maximum height?
	\vfill
	\item What is its maximum  height?
	\vfill
	\item When does the projectile hit the ground?
	\vfill
	\item What what velocity does it hit the ground?
	\vfill
	\end{enumerate}
\item A tank holds 1000 gallons of a fluid, which drains from the bottom of the tank in 30 minutes. The function below give the volume of fluid remaining in the tank after $t$ minutes:
$$V(t)=1000 \left( 1-\frac{1}{30}t \right)^2 \text{  for   } 0 \leq y \leq 30$$
Find  the rate at which the fluid is draining from the tank after 10 minutes. When is the fluid flowing the fastest? Slowest?
\vspace{2.5in}
\end{enumerate}
\end{document}