
\documentclass[11pt,fleqn]{article} 
\usepackage[margin=0.8in, head=0.8in]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx, pgfplots} 
\usepackage[all]{xy}
\usepackage{polynom} 
%\usepackage{pdfsync} %% I don't know why this messes up tabular column widths
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}

\pgfplotsset{compat=1.6}

\pgfplotsset{soldot/.style={color=black,only marks,mark=*}} \pgfplotsset{holdot/.style={color=black,fill=white,only marks,mark=*}}
\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
middle, xlabel={$x$}, ylabel={$y$} }}

%axis equal 
\pagestyle{fancy} 
\lfoot{}
\rfoot{Review Midterm I}

\begin{document}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\renewcommand{\d}{\displaystyle}

\vspace*{-0.7in}

%%%%%%%%%intro page
\begin{center}
  \large
  \sc{Review for Midterm I}\\
\end{center}
\noindent\textbf{Logistics}\\

You will have 90 minutes to take the midterm. You can see what your midterm will look like by going to the public webpage and looking at Midterm I from previous years. Note that your midterm will not be longer then those of previous years\\

\url{https://uaf-math251.github.io/exams.html}\\

You may bring a single 3 x 5 notecard, hand-written, front and back. You may not use a calculator. (There are not problems that require the use of one.)\\

\textbf{For Dr. McIntyre's Section:} Our midterm will start promptly at 9:45 am and will end at 11:15 am.  Some students will finish early. To ensure that later students don't get an unfair advantage, \emph{all students are required to stay in class until 11:15}. If you know you are someone who finishes early, you should bring something to work on \emph{that does not require typing on your phone, laptop or tablet.}

\textbf{For Dr. Faudree's Section:} Our midterm will start promptly at 11:30am.  Once you have finished your midterm, you may leave quietly.\\

\noindent\textbf{Taking a Math Test}

\begin{itemize}
\item The only way to earn partial credit for incorrect answers is by writing explanatory work.
\item Explanatory work needs to be written in a way that a reader can follow it.
\item Write things that are incorrect will generally result in a loss of points. So if something shouldn't be graded, cross it out.
\end{itemize}


\noindent\textbf{Topics}\\

\noindent \fbox{Section 2.1}\\
Secant lines and tangent lines. Average velocity and instantaneous velocity. Average rate of change and instantaneous rate of change.\\

\noindent Examples: \\
(a) Sketch the graph $y=x^3+1.$ Find the secant line between the points on the graph where $x=1$ and $x=3.$ Sketch the secant line on the graph. Find an equation of the tangent line to the graph at $x=1$ and sketch it on the graph. (NOTE: We get to answer the second part of this question using our knowledge of the derivative!) \\
(b) A salmon is swimming up stream and the position of the salmon is given by the function $d(t)=\frac{1}{2}t^2-t$ where $t$ is measured in hours and $d$ is measured in feet. Find the average velocity of the salmon over the interval from $t=2$ to $t=4.$ Find the instantaneous velocity of the salmon at $t=3.$ Include units. Explain in simple terms, in the context of the problem, what these calculations mean.\\

\noindent \fbox{Section 2.2}\\
Be able to evaluate one-sided and two-sided limits from a graph. Vertical asymptotes and limits.\\

\noindent Examples: \\
(a) Sketch a graph with \emph{all} of the following properties: \\
\begin{itemize}
\item $f(x)$ is defined for all real numbers. (ie its domain is $(-\infty,\infty).$
\item $\lim_{x \to 1^-} f(x) = 0,$ $\lim_{x \to 1^+} f(x) =4,$ $f(1) =4$
\item $\lim_{x \to 3} f(x) =4,$ $f(4)=-1.$
\item $\lim_{x \to -1^-} f(x) =\infty$
\end{itemize}
(b) Determine where the graph of $f(x)=\frac{x}{(x+2)^2}$ has a vertical asymptote and use limits to justify your answer is correct. \\

\noindent \fbox{Section 2.3}\\
Evaluating limits algebraically. You need to remember the strategies (factor, common denominator, and rationalizing). But, don't forget to always try simple first: plug in. \\

\noindent Examples: Evaluate $\d \lim_{x \to 9} \frac{3-\sqrt{x}}{9-x}$ and $\d \lim_{x \to 1/2^+} \frac{4x^2-18x}{2x-1}$\\

\noindent \fbox{Section 2.4}\\
Continuity. From a graph, determine where a graph is or is not continuous. From an algebraic description of a function, determine where a function is or is not continuous. Be able to explain why a function is not continuous at a point. Use the Intermediate Value Theorem.\\

\noindent Examples: 
(a) Look at your graph from Section 2.2. Where does it fail to be continuous and why? \\
(b) Determine where the functions $f(x)= \frac{3-\sqrt{x}}{9-x}$ and $g(x)=  \frac{4x^2-18x}{2x-1}$ fail to be continuous and show that your answer is correct algebraically.\\
(c) Use the Intermediate Value Theorem to show that the equation $2e^x-3x-5=0$ has a solution.\\

\noindent \fbox{Section 3.1}\\
The relationship between secant lines and the derivative.\\

\noindent Example: Explain what the expression $f'(a) = \lim_{x \to a} \frac{f(x)-f(a)}{x-a}$ means in terms of secant lines, tangent lines and the derivative. Draw a picture to illustrate you idea.\\

\noindent \fbox{Section 3.2}\\
The derivative as a function. The formal definition of the derivative. The relationship between the graph of $f(x)$ and the graph of $f'(x).$\\

\noindent Example: Sketch the derivative of your graph from the Section 2.2 example. Use the definition of the derivative to find $f'(x)$ for $f(x)=1/x^2.$\\

\noindent \fbox{Section 3.3}\\
Derivative rules: power, constant, sum/difference, product, quotient, and the derivatives of the sine and cosine functions.\\

\noindent Example: Find the derivative of $y=2x^{0.05}-\frac{x}{10}+\frac{\cos(x)}{5}$, $s=t\cos(t),$ and $f(x)=\frac{x^3}{1-x}+ \sin(x)$\\

\noindent \fbox{Section 3.4}\\
The derivative as a rate of change. Interpretations of the derivative. Velocity and acceleration.\\

\noindent Example: Assume the distance traveled by a snow machine on a straight trail is given by $s(t)$ where $t$ is in hours starting at 12 noon and $s$ is in miles. Interpret $s'(4)=10.$ Interpret $s(4)-s(0).$ Interpret $(s(4)-s(1))/(4-1).$ Using the fact that that $s''(4)=-1.2,$ estimate $s'(4.5).$

\end{document}

